Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-07-06 manuscript/appendix.Rmd
updated appendix

>>>>

\newpage
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S3 <- read.csv("tables_figures/best_models_each_flux.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S3, format = "latex", booktabs = TRUE, caption = "Table S5. Best models by carbon flux. Models where delta AIC </= 2 are presented", escape = F) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  collapse_rows(columns = 1)

```
